Dependently Typed Multi-stage Calculus

### 2019-11-26 slides/main.tex
Spell check.

\begin{frame}[fragile]{Example of Multi-stage Programming in MetaOCaml}
    \begin{center}
        \begin{verbatim}
 # let a = .< (1 + 2) >.;;
 val a : int code = .< (1 + 2) >.
 # run a;;
 - : int = 3

 # let b = .<(.~a) + (.~a)>.;;
 val b : int code = .< ((1 + 2) + (1 + 2)) >. 
 # run b;;
 - : int = 6
        \end{verbatim}
    \end{center}
    \note{
    }
\end{frame}

@@

    \begin{verbatim}
 val vadd-gen : Int -> (Vec -> Vec -> Vec) code
 # let vadd3 = vadd-gen 3;;
 val vadd3 : (Vec -> Vec -> Vec) code
 (* vadd3 v w =                            *)
 (*   < let (v, w)=(~v, ~w) in             *)
 (*      [v[0]+w[0];v[1]+w[1];v[2]+w[2]] > *)
    \end{verbatim}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{The problem of vadd3 generated by vadd-gen}
    Runtime error occurs for wrong length vectors.
    \begin{verbatim}
 val vadd3 : (Vec -> Vec -> Vec) code
 # (run vadd3) [1;2;3] [4;5;6];;
 - : Vec = [5;7;9]
 # (run vadd3) [1;2] [4;5];;
 Exception: Failure
    \end{verbatim}
    \note{
    }
\end{frame}

@@

 # (run vadd3) [1;2] [4;5];;
 [1;2] has type Vec 2
 but was expected of type Vec 3
 \end{verbatim}
    \note{
        By the way, we can write types dependent on values using dependent types.
    }
\end{frame}

@@

    Typing judgements of \LTP include a stage.
    \begin{center}
    \( \G \vdash 2 + 3 : \I @ 1 \)
    \end{center}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Typing Rules of \LMD}
    Cannot apply a term to a function in a different stage.
    \begin{center}
        {\small \infrule[\TApp]{
            \G\V M:\sigma \to \tau @ n \andalso
            \G\V N:\sigma @ n
        }{
            \G\V M\ N : \tau @ n
        }}
    \end{center}
    Increase and decrease stage using \( \TB \) and \( \TBL \).
    \begin{center}
        {\small \infrule[{\TTB}]{
            \G\V M:\tau @ n+1
        }{
            \G\V\TB M:\TW \tau @ n
        } \hfil
        \infrule[{\TTBL}]{
            \G\V M:\TW \tau @ n
        }{
            \G\V\TBL M:\tau @ n + 1
        }}
    \end{center}
    \note{
        Let's have a look on some typing rules.
    }
\end{frame}

\begin{frame}[fragile]{Cross Stage Persistence (CSP)}
    Enable using terms at lower stages at higer stages. \\[3mm]

@@

\begin{frame}[fragile]{Types of \LMD}
    \begin{block}{Types}
    \begin{tabbing}
        \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
        \> \( \mid \TW\ \tau \) \> (code type) \\
        \> \( \bm{\mid \Pi x:\tau.\tau} \) \> (function dependent type) \\
        \> \( \bm{\mid \tau\ M} \) \> (application, e.g. \(\text{Vec}\ 3\))
    \end{tabbing}
    \end{block}
    Note: We need CSP to use normal variables in code types.
    \begin{itemize}
        \item OK  \( \Pi n: \TW (\text{Vec}\ \%n) \)
        \item NG  \( \Pi n: \TW (\text{Vec}\ n) \)
    \end{itemize}
   \note{
    }
\end{frame}

@@

\begin{frame}[fragile]{Related Works}
    \begin{itemize}
        \item \LTP [Hanada\&Igarashi'14]
            \begin{itemize}
                \item Multi-stage programming including explicit CSP
            \end{itemize}
        \item Concoqtion [Forgarty et al]
            \begin{itemize}
                \item Introduce indexed type into MetaOCaml.
            \end{itemize}
    \end{itemize}
    \note{
    }
\end{frame}

@@

% \begin{frame}[fragile]{Types of \LMD}
%     \begin{block}{Types}
%     \( \tau,\sigma ::= X \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
%     \end{block}
%     \begin{itemize}
%         \item \( X \): type-level constants 
%             \begin{itemize}
%                 \item \( \text{Vec} \), \( \text{Int} \).
%             \end{itemize}
%         \item \( \Pi x:\tau.\sigma \): dependent type.
%         \item \( \tau\ M \): Application of term to dependent type.
%             \begin{itemize}
%                 \item \( \text{Vec } 3 \)
%             \end{itemize}
%         \item \( \TW_{\alpha} \tau \): a type of code of type \( \tau \).
%             \begin{itemize}
%                 \item \( \text{vadd-gen 3} : \TW_\alpha (\text{Vec}\ 3 \to \text{Vec}\ 3 \to \text{Vec}\ 3) \)
%             \end{itemize}
%     \end{itemize}
%     \note{
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Kinds of \LMD}
%     \begin{block}{Kinds}
%         \( K ::= * \mid \Pi x:\tau.K \)
%     \end{block}
%     \begin{itemize}
%         \item \( * \): kind of proper type
%             \begin{itemize}
%                 \item \( \text{Int} :: * \)
%             \end{itemize}
%         \item \( \Pi x:\tau.K \): kind dependent on term.
%             \begin{itemize}
%                 \item \( \text{Vec} :: (\Pi x:\text{Int}.*) \)
%             \end{itemize}
%     \end{itemize}
%     \note{
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Judgements of \LMD}
%     \begin{itemize}
%         \item \( \G \V K @ A \)
%             \begin{itemize}
%                 \item \( K \) is a proper kind under signature \( \Sigma \) at stage \( A \).
%             \end{itemize}
%         \item \( \G \V \tau :: K @ A \)
%             \begin{itemize}
%                 \item Type \( \tau \) has kind \( K \) under signature \( \Sigma \) at stage \( A \).
%             \end{itemize}
%         \item \( \G \V M : \tau @ A \)
%         \item \( \G \V K \E K' @ A \)
%             \begin{itemize}
%                 \item Kind \( K \) is equivalent to \( K' \) under signature \( \Sigma \) at stage \( A \).
%             \end{itemize}
%         \item \( \G \V \tau \E \tau' @ A \)
%         \item \( \G \V M \E M' @ A \)
%     \end{itemize}
%     \note{
%     }
% \end{frame}
%
% \begin{frame}[fragile]{What is stage\ \( A \)\ ?}
%     % I copied this underwrite macro from
%     % https://tex.stackexchange.com/questions/141932/how-to-write-under-an-underline.
%     % \underwrite[<thickness>]{<numerator>}{<denominator>}
%     \newcommand{\underwrite}[3][]{
%         \genfrac{}{}{#1}{}{\textstyle #2}{\textstyle #3}
%     }
%
%     Level of nested brankets
%     \begin{block}{Stages}
%         \( A := \varepsilon (\text{empty}) \mid \alpha \mid A\alpha \)
%     \end{block}
%     \begin{center}
%         \( \underbrace{(\textbf{run}\ (\TB_\alpha\ \overbrace{(2 + 3)}^{\let\scriptstyle\textstyle\substack{@\alpha}})) + 1}_{\let\scriptstyle\textstyle\substack{@\varepsilon}} \)
%     \end{center}
%     \note{
%         Stage is a sequence of stage variables which appended to each brack triangles.
%         \( \varepsilon \) means the empty sequence
%
%         The wholes expression is a term on stage \( \varepsilon \),
%         But subexpression in the brack triangle is a term on stage \( \alpha \).
%     }
% \end{frame}
%
% \begin{frame}[fragile]{What is signature \( \Sigma \)\ ?}
%     Signature \( \Sigma \) is a sequence of type-level constants and constant values.
%     \begin{itemize}
%         \item For example,
%             \begin{itemize}
%                 \item \( \Sigma = \text{Int}::*, \text{Vec}::\Pi x:\text{Int}.*, 0:\text{Int} \)
%             \end{itemize}
%         \item Elements of \( \Sigma \) can be used at any stages.
%     \end{itemize}
%     \note{
%         自然数が無限個あるというツッコミを誘発する気がする。
%         後者関数が存在することにするか?
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Typing Rules of \LMD}
%     \begin{center}
%         \infrule[{\TTB}]{
%             \G\V M:\tau@{A\alpha}
%         }{
%             \G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A
%         } \\[2mm]
%         \infrule[{\textsc{T-App}}]{
%             \G\V M:(\Pi (x:\sigma).\tau)@A \andalso
%             \G\V N:\sigma@A
%         }{
%             \G\V M\ N : \tau[x\mapsto N]@A
%         } \\[2mm]
%         \infrule[{\TConst}]{
%             c:\tau \in \Sigma \andalso
%         }{
%             \G \V c:\tau@A
%         }
%     \end{center}
%     \begin{itemize}
%         \item Terms are stage sensitive so cannot ignore stages.
%         \item Constants in \( \Sigma \) can be used at any stages.
%     \end{itemize}
%     \note{
%         Let's have a look on some typing rules.
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Kinding Rules of \LMD}
%     \begin{center}
%         \infrule[{\KTW}]{
%             \G\V \tau::*@A\alpha
%         }{
%             \G\V\TW_\alpha \tau::*@A
%         }\\[2mm]
%         \infrule[{\KApp}]{
%             \G\V \sigma:: (\Pi x:\tau.K)@A \andalso \G\V M:\tau@A
%         }{
%             \G\V \sigma\ M::K[x\mapsto M]@A
%         }
%         \infrule[{\KTConst}]{
%             X::K \in \Sigma
%         }{
%             \G \V X::K@A
%         }
%     \end{center}
%     \begin{itemize}
%         \item Types are also stage sensitive.
%         \item Type-level constants in \( \Sigma \) can be used at any stages.
%     \end{itemize}
%     \note{
%         Kinding rules have something in common with typing rules.
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Example of Kinding Derivation}
%     \renewcommand{\Vec}{\text{Vec}}
%     \( \V \TB_\alpha [1,2,3] : \underbrace{\TW_\alpha (\Vec\ 3)}_{\TW_\alpha (\Vec\ 3) :: * @ \varepsilon} @ \varepsilon \) \\[2mm]
%     \pause
%     \( \Sigma = \Vec::\Pi x:\I.*, 0:\I, 1:\I, \cdots \)
%     \begin{center}
%         \footnotesize
%         \begin{minipage}{0.7\hsize}
%             \infer[\KTW]
%             {\V \TW_\alpha (\Vec\ 3) :: * @ \varepsilon}
%             {
%                 \infer[\KApp]
%                 {\V \Vec\ 3 :: * @ \alpha}
%                 {
%                     \infer[\KTConst]
%                     {\V \Vec :: \Pi x:\I.* @ \alpha}
%                     {\Vec :: \Pi x:\I.* \in \Sigma}
%                     \andalso
%                     \infer[\TConst]
%                     {\V 3 : \I @ \alpha}
%                     {3 : \I \in \Sigma}
%                 }
%             }
%         \end{minipage}
%     \end{center}
%     We can use \Vec\ and integers at any stages.
%     \note{
%         The constructed type Vec 3 is stage sensitive so we cannot use at arbitrary stages
%         but the elements, Vec and 3 are in the signature \( \Sigma \) and can be used at any stages.
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Type and Term Equality Rules of \LMD}
%     \begin{center}
%         \footnotesize{
%             \infrule[{\QTApp}]{
%                 \G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso
%                 \G\V M \E N : \rho @A
%             }{
%                 \G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A
%             } \\[2mm]
%             \infrule[{\QBeta}]{
%                 \G,x:\sigma@A\V M:\tau@A \andalso
%                 \G\V N:\sigma@A
%             }{
%                 \G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A
%             } \\[2mm]
%             \infrule[{\QPercent}]{
%                 \G\V M:\tau@{A\alpha} \andalso
%                 \G\V M:\tau@A
%             }{
%                 \G\V\%_\alpha M \E M : \tau@{A\alpha}
%             } \\[2mm]
%             \infrule[{\textsc{T-Conv}}]{
%                 \G\V M:\tau@A \andalso
%                 \G\V \tau\equiv \sigma :: K@A
%             }{
%                 \G\V M:\sigma@A
%             }
%         }
%     \end{center}
%     \note{
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Examples of Type Equality}
%     \renewcommand{\V}{\text{Vec}}
%     \begin{itemize}
%         \item \( (\lambda x:\text{Int}.x)\ 3\E 3 \)
%             \begin{itemize}
%                 \item From \QBeta.
%             \end{itemize}
%         \item \( \V\ ((\lambda x:\text{Int}.x)\ 3) \E \V\ 3 \)
%             \begin{itemize}
%                 \item From \QTApp and \QBeta.
%             \end{itemize}
%         \item \( \V\ (\%_\alpha 3) \E \V\ 3 \)
%             \begin{itemize}
%                 \item Because \( 3 \) has type \text{Int} at any stage, we can use \QPercent.
%             \end{itemize}
%     \end{itemize}
%     \note{
%         Shold I show complete derivation tree?
%     }
% \end{frame}

>>>>

\begin{frame}[fragile]{Example of Multi-stage Programming in MetaOCaml}
    \begin{center}
        \begin{verbatim}
 # let a = < (1 + 2) >;;
 val a : int code = < (1 + 2) >
 # run a;;
 - : int = 3

 # let b = <(~a) + (~a)>
 val b : int code = < ((1 + 2) + (1 + 2)) >
 # run b
 - : int = 6
        \end{verbatim}
    \end{center}
    \note{
    }
\end{frame}

@@

    \begin{verbatim}
 val vadd-gen : Int -> (Vec -> Vec -> Vec) code
 # let vadd3 = vadd-gen 3
 val vadd3 : (Vec -> Vec -> Vec) code
 (* vadd3 v w =                            *)
 (*   < let (v, w)=(~v, ~w) in             *)
 (*      [v[0]+w[0];v[1]+w[1];v[2]+w[2]] > *)
    \end{verbatim}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{The problem of vadd3 generated by vadd-gen}
    Runtime error occurs for wrong length vectors.
    \begin{verbatim}
 val vadd3 : (Vec -> Vec -> Vec) code
 # (run vadd3) [1;2;3] [4;5;6]
 - : Vec = [5;7;9]
 # (run vadd3) [1;2] [4;5]
 Exception: Failure
    \end{verbatim}
    \note{
    }
\end{frame}

@@

 # (run vadd3) [1;2] [4;5]
 [1;2] has type Vec 2
 but was expected of type Vec 3
 \end{verbatim}
    \note{
        By the way, we can write types dependent on values using dependent types.
    }
\end{frame}

@@

    Typing judgements of \LTP include a stage.
    \begin{center}
        \( \G \vdash 2 + 3 : \I {\mathbf{@ 1}} \)
    \end{center}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Typing Rules of \LTP}
    Cannot apply a term to a function in a different stage.
    \begin{center}
        {\small \infrule[\TApp]{
            \G\V M:\sigma \to \tau @ n \andalso
            \G\V N:\sigma @ n
        }{
            \G\V M\ N : \tau @ n
        }}
    \end{center}
    Increase and decrease stage using \( \TB \) and \( \TBL \).
    \begin{center}
        {\small \infrule[{\TTB}]{
            \G\V M:\tau @ n+1
        }{
            \G\V\TB M:\TW \tau @ n
        } \hfil
        \infrule[{\TTBL}]{
            \G\V M:\TW \tau @ n
        }{
            \G\V\TBL M:\tau @ n + 1
        }}
    \end{center}
    In general, we cannot use terms of one stage at other stages.
    \note{
        Let's have a look on some typing rules.
    }
\end{frame}

\begin{frame}[fragile]{Cross Stage Persistence (CSP)}
    Enable using terms at lower stages at higher stages. \\[3mm]

@@

\begin{frame}[fragile]{Types and Kinds of \LMD}
    Append function dependent types to types of \LTP.
    \begin{block}{Types}
        \begin{tabbing}
            \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
            \> \( \mid \TW\ \tau \) \> (code type) \\
            \> \( \bm{\mid \Pi x:\tau.\tau} \) \> (function dependent type) \\
            \> \( \bm{\mid \tau\ M} \) \> (application, e.g. \(\text{Vec}\ 3\))
        \end{tabbing}
    \end{block}
    \begin{block}{Kinds}
        \( K ::= * \mid \Pi x:\tau.K \)
    \end{block}
    % Note: We need CSP to use normal variables in code types.
    % \begin{itemize}
    %     \item OK  \( \Pi n: \TW (\text{Vec}\ \%n) \)
    %     \item NG  \( \Pi n: \TW (\text{Vec}\ n) \)
    % \end{itemize}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Kinding rules of \LMD}
    Types have also stages because types may contains terms.
    \begin{center}
    \infrule[{\KApp}]{
        \G\V \sigma:: (\Pi x:\tau.K) @ n \andalso \G\V M:\tau @ n
    }{
        \G\V \sigma\ M::K[x\mapsto M] @ n
    }
    \infrule[{\KAbs}]{
        \G\V \tau :: * @ n \andalso \G,x:\tau@ n \V \sigma::J@A
    }{
        \G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J) @ n
    }
    \end{center}
    So, we need CSP in types also.
    \begin{center}
    \( \underbrace{\Pi n:\I. \TW (\overbrace{\text{Vec}\ \%n}^{\text{stage }1})}_{\text{stage }0} \)
    \end{center}
\end{frame}

\begin{frame}[fragile]{Constants and type-level constants of \LMD}
    Constants and type-level constants can be used at any stage.
    \begin{itemize}
        \item Integers: \( 0,1,2,3,\dots \)
        \item Int, Vec, \dots
    \end{itemize}

    \begin{tabbing}
        \hspace{5mm} \= \text{val doub3} : \( \text{Vec }3 \to \text{Vec }3 \) \\[2mm]
        \> \textbf{let } \text{double} = \( \TB (\% \text{doub3}) \) \\
        \> \text{val double} : \( \TW ( \text{Vec }3 \to \text{Vec }3) \)
    \end{tabbing}
\end{frame}

@@

\begin{frame}[fragile]{Related Work}
    \begin{itemize}
        \item \LTP [Hanada\&Igarashi'14]
            \begin{itemize}
                \item Multi-stage programming including explicit CSP
            \end{itemize}
        \item Concoqtion [Forgarty et al.]
            \begin{itemize}
                \item Introduce indexed type into MetaOCaml.
                \item Types are indexed by Coq terms.
            \end{itemize}
    \end{itemize}
    \note{
    }
\end{frame}

@@

% \begin{frame}[fragile]{Types of \LMD}
%     \begin{block}{Types}
%     \( \tau,\sigma ::= X \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
%     \end{block}
%     \begin{itemize}
%         \item \( X \): type-level constants 
%             \begin{itemize}
%                 \item \( \text{Vec} \), \( \text{Int} \).
%             \end{itemize}
%         \item \( \Pi x:\tau.\sigma \): dependent type.
%         \item \( \tau\ M \): Application of term to dependent type.
%             \begin{itemize}
%                 \item \( \text{Vec } 3 \)
%             \end{itemize}
%         \item \( \TW_{\alpha} \tau \): a type of code of type \( \tau \).
%             \begin{itemize}
%                 \item \( \text{vadd-gen 3} : \TW_\alpha (\text{Vec}\ 3 \to \text{Vec}\ 3 \to \text{Vec}\ 3) \)
%             \end{itemize}
%     \end{itemize}
%     \note{
%     }
% \end{frame}

% \begin{frame}[fragile]{Kinds of \LMD}
%     \begin{block}{Kinds}
%         \( K ::= * \mid \Pi x:\tau.K \)
%     \end{block}
%     \begin{itemize}
%         \item \( * \): kind of proper type
%             \begin{itemize}
%                 \item \( \text{Int} :: * \)
%             \end{itemize}
%         \item \( \Pi x:\tau.K \): kind dependent on term.
%             \begin{itemize}
%                 \item \( \text{Vec} :: (\Pi x:\text{Int}.*) \)
%             \end{itemize}
%     \end{itemize}
%     \note{
%     }
% \end{frame}

% \begin{frame}[fragile]{Judgements of \LMD}
%     \begin{itemize}
%         \item \( \G \V K @ A \)
%             \begin{itemize}
%                 \item \( K \) is a proper kind under signature \( \Sigma \) at stage \( A \).
%             \end{itemize}
%         \item \( \G \V \tau :: K @ A \)
%             \begin{itemize}
%                 \item Type \( \tau \) has kind \( K \) under signature \( \Sigma \) at stage \( A \).
%             \end{itemize}
%         \item \( \G \V M : \tau @ A \)
%         \item \( \G \V K \E K' @ A \)
%             \begin{itemize}
%                 \item Kind \( K \) is equivalent to \( K' \) under signature \( \Sigma \) at stage \( A \).
%             \end{itemize}
%         \item \( \G \V \tau \E \tau' @ A \)
%         \item \( \G \V M \E M' @ A \)
%     \end{itemize}
%     \note{
%     }
% \end{frame}

% \begin{frame}[fragile]{What is stage\ \( A \)\ ?}
%     % I copied this underwrite macro from
%     % https://tex.stackexchange.com/questions/141932/how-to-write-under-an-underline.
%     % \underwrite[<thickness>]{<numerator>}{<denominator>}
%     \newcommand{\underwrite}[3][]{
%         \genfrac{}{}{#1}{}{\textstyle #2}{\textstyle #3}
%     }
%
%     Level of nested brankets
%     \begin{block}{Stages}
%         \( A := \varepsilon (\text{empty}) \mid \alpha \mid A\alpha \)
%     \end{block}
%     \begin{center}
%         \( \underbrace{(\textbf{run}\ (\TB_\alpha\ \overbrace{(2 + 3)}^{\let\scriptstyle\textstyle\substack{@\alpha}})) + 1}_{\let\scriptstyle\textstyle\substack{@\varepsilon}} \)
%     \end{center}
%     \note{
%         Stage is a sequence of stage variables which appended to each brack triangles.
%         \( \varepsilon \) means the empty sequence
%
%         The wholes expression is a term on stage \( \varepsilon \),
%         But subexpression in the brack triangle is a term on stage \( \alpha \).
%     }
% \end{frame}

% \begin{frame}[fragile]{What is signature \( \Sigma \)\ ?}
%     Signature \( \Sigma \) is a sequence of type-level constants and constant values.
%     \begin{itemize}
%         \item For example,
%             \begin{itemize}
%                 \item \( \Sigma = \text{Int}::*, \text{Vec}::\Pi x:\text{Int}.*, 0:\text{Int} \)
%             \end{itemize}
%         \item Elements of \( \Sigma \) can be used at any stages.
%     \end{itemize}
%     \note{
%         自然数が無限個あるというツッコミを誘発する気がする。
%         後者関数が存在することにするか?
%     }
% \end{frame}

% \begin{frame}[fragile]{Typing Rules of \LMD}
%     \begin{center}
%         \infrule[{\TTB}]{
%             \G\V M:\tau@{A\alpha}
%         }{
%             \G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A
%         } \\[2mm]
%         \infrule[{\textsc{T-App}}]{
%             \G\V M:(\Pi (x:\sigma).\tau)@A \andalso
%             \G\V N:\sigma@A
%         }{
%             \G\V M\ N : \tau[x\mapsto N]@A
%         } \\[2mm]
%         \infrule[{\TConst}]{
%             c:\tau \in \Sigma \andalso
%         }{
%             \G \V c:\tau@A
%         }
%     \end{center}
%     \begin{itemize}
%         \item Terms are stage sensitive so cannot ignore stages.
%         \item Constants in \( \Sigma \) can be used at any stages.
%     \end{itemize}
%     \note{
%         Let's have a look on some typing rules.
%     }
% \end{frame}

% \begin{frame}[fragile]{Kinding Rules of \LMD}
%     \begin{center}
%         \infrule[{\KTW}]{
%             \G\V \tau::*@A\alpha
%         }{
%             \G\V\TW_\alpha \tau::*@A
%         }\\[2mm]
%         \infrule[{\KApp}]{
%             \G\V \sigma:: (\Pi x:\tau.K)@A \andalso \G\V M:\tau@A
%         }{
%             \G\V \sigma\ M::K[x\mapsto M]@A
%         }
%         \infrule[{\KTConst}]{
%             X::K \in \Sigma
%         }{
%             \G \V X::K@A
%         }
%     \end{center}
%     \begin{itemize}
%         \item Types are also stage sensitive.
%         \item Type-level constants in \( \Sigma \) can be used at any stages.
%     \end{itemize}
%     \note{
%         Kinding rules have something in common with typing rules.
%     }
% \end{frame}

% \begin{frame}[fragile]{Example of Kinding Derivation}
%     \renewcommand{\Vec}{\text{Vec}}
%     \( \V \TB_\alpha [1,2,3] : \underbrace{\TW_\alpha (\Vec\ 3)}_{\TW_\alpha (\Vec\ 3) :: * @ \varepsilon} @ \varepsilon \) \\[2mm]
%     \pause
%     \( \Sigma = \Vec::\Pi x:\I.*, 0:\I, 1:\I, \cdots \)
%     \begin{center}
%         \footnotesize
%         \begin{minipage}{0.7\hsize}
%             \infer[\KTW]
%             {\V \TW_\alpha (\Vec\ 3) :: * @ \varepsilon}
%             {
%                 \infer[\KApp]
%                 {\V \Vec\ 3 :: * @ \alpha}
%                 {
%                     \infer[\KTConst]
%                     {\V \Vec :: \Pi x:\I.* @ \alpha}
%                     {\Vec :: \Pi x:\I.* \in \Sigma}
%                     \andalso
%                     \infer[\TConst]
%                     {\V 3 : \I @ \alpha}
%                     {3 : \I \in \Sigma}
%                 }
%             }
%         \end{minipage}
%     \end{center}
%     We can use \Vec\ and integers at any stages.
%     \note{
%         The constructed type Vec 3 is stage sensitive so we cannot use at arbitrary stages
%         but the elements, Vec and 3 are in the signature \( \Sigma \) and can be used at any stages.
%     }
% \end{frame}

% \begin{frame}[fragile]{Type and Term Equality Rules of \LMD}
%     \begin{center}
%         \footnotesize{
%             \infrule[{\QTApp}]{
%                 \G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso
%                 \G\V M \E N : \rho @A
%             }{
%                 \G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A
%             } \\[2mm]
%             \infrule[{\QBeta}]{
%                 \G,x:\sigma@A\V M:\tau@A \andalso
%                 \G\V N:\sigma@A
%             }{
%                 \G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A
%             } \\[2mm]
%             \infrule[{\QPercent}]{
%                 \G\V M:\tau@{A\alpha} \andalso
%                 \G\V M:\tau@A
%             }{
%                 \G\V\%_\alpha M \E M : \tau@{A\alpha}
%             } \\[2mm]
%             \infrule[{\textsc{T-Conv}}]{
%                 \G\V M:\tau@A \andalso
%                 \G\V \tau\equiv \sigma :: K@A
%             }{
%                 \G\V M:\sigma@A
%             }
%         }
%     \end{center}
%     \note{
%     }
% \end{frame}

% \begin{frame}[fragile]{Examples of Type Equality}
%     \renewcommand{\V}{\text{Vec}}
%     \begin{itemize}
%         \item \( (\lambda x:\text{Int}.x)\ 3\E 3 \)
%             \begin{itemize}
%                 \item From \QBeta.
%             \end{itemize}
%         \item \( \V\ ((\lambda x:\text{Int}.x)\ 3) \E \V\ 3 \)
%             \begin{itemize}
%                 \item From \QTApp and \QBeta.
%             \end{itemize}
%         \item \( \V\ (\%_\alpha 3) \E \V\ 3 \)
%             \begin{itemize}
%                 \item Because \( 3 \) has type \text{Int} at any stage, we can use \QPercent.
%             \end{itemize}
%     \end{itemize}
%     \note{
%         Shold I show complete derivation tree?
%     }
% \end{frame}
